Credit Risk Distribution and Capital Savings

### 2020-04-02 Analysis/Draft/Draft_bookdown.Rmd
Add new markdown file for draft (using bookdown)

---
title: "Credit Risk Distribution and Capital Savings"
author:
- name: Lucas Avezum
  affiliation: CentER and EBC, Tilburg University; l.avezum@uvt.nl; +31134664531;  Warandelaan 2, 5037 AB Tilburg, NL, The Netherlands 
date: 
header-includes:
   - \usepackage{rotating, graphicx, dcolumn, longtable, float}
output:
  pdf_document:
    #citation_package: natbib
    latex_engine: pdflatex
    template: tex-ms.tex
    fig_caption: true
  html_document:
    df_print: paged
  word_document: default
bibliography: ../../Auxiliar/mybibfile.bib
csl: ../../Auxiliar/cambridge-journal-of-economics.csl
citecolor: black
anonymous: false
fontsize: 11pt
spacing: "double"
geometry: margin= 1in
keywords: Internal ratings-based models, Risk-weighted assets dispersion, Procyclicality
JEL: G21, G28, G11
linkcolor: black
biblio-style: apsr
subtitle: ''
thanks: Preliminary draft.  
abstract: "The Basel II accord introduced a concave mapping from probabilities of default (PD) to capital requirements for banks adopting the internal ratings-based (IRB) approach. Therefore, total capital requirements depends not only on the portfolio's average PD but also on the shape of its PD distribution. Using a hand-collected dataset, I propose a method that decomposes the contribution of the PD distribution to capital requirements into an average component and a shape component. While a larger average component increases capital charges, a larger shape component generates capital savings. I document that these capital savings are important sources of risk-weight variability across banks. I further investigate the relationship of capital savings with the business cycle and find it to be countercyclical. The results suggest that a recalibration of the current IRB framework can significantly reduce the procyclicality of capital requirements."
urlcolor: black
---

@@

## Other Determinants of Capital Savings and Summary Statistics

@@

Lastly, the method that I proposed to measure the shape component of the PD distribution could be flawed. In Table \ref{tab3} I use the well-known Gini coefficient to measure the shape component of the PD distribution. Again, the results shown in Table \ref{tab3} suppport the evidence from the last three tables: *Capital savings* are countercyclical and mostly driven by the effect of GDP growth rate on *Capital savings* from corporate portfolios.

@@

@@

# Policy Discussion: Using Capital Savings to Reduce Capital Ratio Procyclicality

@@

@@

<!-- <div id="refs"></div> -->

@@

<!-- \begin{table}[!htbp] \centering  -->
<!--   \caption{Cyclicality of Capital Savings}  -->
<!--   \label{tab1}  -->
<!-- \small  -->
<!-- \begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3}}  -->
<!-- \hline  -->
<!-- \hline \\[-1.8ex]  -->
<!-- \\[-1.8ex] & \multicolumn{3}{c}{States}  & \multicolumn{2}{c}{$\Delta$ Initial}  \\ \cline{2-4}\cline{5-6} -->
<!-- \\[-1.8ex] & \multicolumn{1}{c}{Initial} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} \\  -->
<!-- \hline \\[-1.8ex]  -->
<!--  $\text{RWA}$  & 63.88 & 94.21 & 90.29 & 30.32 & 26.42 \\  -->
<!--   $\text{RWA}^c$ & 64.65 & 94.65 & 94.65 & 29.96 & 29.96  \\  -->
<!--   $\text{RWA}^s$ & 0.81 & 0.45 & 4.35 & -0.36 & 3.54  \\  -->
<!--   \hline \\[-1.8ex] -->
<!--  Avg. PD & 0.15\% & 0.25\% & 0.25\% &  &   \\  -->
<!--   S.d. PD & 0.05\% & 0.05\% & 0.23\% &  &   \\  -->
<!-- \hline \\[-1.8ex]  -->
<!-- \end{tabular}  -->
<!-- \end{table}  -->
```{r winsorized_data, fig.height = 10, fig.width = 7, results="asis",out.width = "1\\textwidth"}
## Set winsorizing limits
p_w <- c(0.05, 0.95)        
bank.data.win <- bank.data %>% 
  ungroup()%>%
  filter(!is.na(RW.s), bvdid %in% pillar3.data$bvdid) %>% 
  mutate_if(is.numeric,Winsorize,probs = p_w ,na.rm = TRUE)%>%
  group_by(bvdid)

@@

>>>>

---
title: "Credit Risk Distribution and Capital Savings"
author:
- affiliation: CentER and EBC, Tilburg University; l.avezum@uvt.nl; +31134664531;  Warandelaan
    2, 5037 AB Tilburg, NL, The Netherlands
  name: Lucas Avezum
date: '\emph{\today}'
output:
  bookdown::pdf_document2:
    fig_caption: yes
    latex_engine: pdflatex
    template: tex-ms.tex
  pdf_document: default
  word_document: default
biblio-style: apsr
bibliography: ../../Auxiliar/mybibfile.bib
citecolor: black
csl: ../../Auxiliar/cambridge-journal-of-economics.csl
anonymous: no
fontsize: 11pt
geometry: margin= 1in
header-includes: \usepackage{rotating, graphicx, dcolumn, longtable, float}
keywords: Internal ratings-based models, Risk-weighted assets dispersion, Procyclicality
linkcolor: black
abstract: The Basel II accord introduced a concave mapping from probabilities of default
  (PD) to capital requirements for banks adopting the internal ratings-based (IRB)
  approach. Therefore, total capital requirements depends not only on the portfolio's
  average PD but also on the shape of its PD distribution. Using a hand-collected
  dataset, I propose a method that decomposes the contribution of the PD distribution
  to capital requirements into an average component and a shape component. While a
  larger average component increases capital charges, a larger shape component generates
  capital savings. I document that these capital savings are important sources of
  risk-weight variability across banks. I further investigate the relationship of
  capital savings with the business cycle and find it to be countercyclical. The results
  suggest that a recalibration of the current IRB framework can significantly reduce
  the procyclicality of capital requirements.
spacing: double
subtitle: ''
thanks: Preliminary draft.
JEL: G21, G28, G11
urlcolor: black
toc: FALSE
---

@@

@@

Lastly,  In Table \ref{tab3} I use the Gini coefficient as an alternative measure of the shape component of the PD distribution. Again, the results shown in Table \ref{tab3} suppport the evidence from the last three tables: *Capital savings* are countercyclical and mostly driven by the effect of GDP growth rate on *Capital savings* from corporate portfolios.

@@

Ideally we want to fix the porfolio at some point in time and compare its and new loans PD distribution. Unfortunately, I cannot track individual assets of a portfolio. In this section I compare moments of the PD distribution between good and bad times without disantangling the direct effect of the business cycle on the distribution from the realocation effect.

@@

@@

# Determinants of Capital Savings

@@

<div id="refs"></div>

@@

<!-- \begin{table}[!htbp] \centering  -->
<!--   \caption{Cyclicality of Capital Savings}  -->
<!--   \label{tab1}  -->
<!-- \small  -->
<!-- \begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3}}  -->
<!-- \hline  -->
<!-- \hline \\[-1.8ex]  -->
<!-- \\[-1.8ex] & \multicolumn{3}{c}{States}  & \multicolumn{2}{c}{$\Delta$ Initial}  \\ \cline{2-4}\cline{5-6} -->
<!-- \\[-1.8ex] & \multicolumn{1}{c}{Initial} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} & \multicolumn{1}{c}{A} & \multicolumn{1}{c}{B} \\  -->
<!-- \hline \\[-1.8ex]  -->
<!--  $\text{RWA}$  & 63.88 & 94.21 & 90.29 & 30.32 & 26.42 \\  -->
<!--   $\text{RWA}^c$ & 64.65 & 94.65 & 94.65 & 29.96 & 29.96  \\  -->
<!--   $\text{RWA}^s$ & 0.81 & 0.45 & 4.35 & -0.36 & 3.54  \\  -->
<!--   \hline \\[-1.8ex] -->
<!--  Avg. PD & 0.15\% & 0.25\% & 0.25\% &  &   \\  -->
<!--   S.d. PD & 0.05\% & 0.05\% & 0.23\% &  &   \\  -->
<!-- \hline \\[-1.8ex]  -->
<!-- \end{tabular}  -->
<!-- \end{table}  -->

```{r winsorized_data, fig.height = 10, fig.width = 7, results="asis",out.width = "1\\textwidth"}
## Set winsorizing limits
p_w <- c(0.05, 0.95)        
bank.data.win <- bank.data %>% 
  ungroup()%>%
  filter(!is.na(RW.s), bvdid %in% pillar3.data$bvdid) %>% 
  mutate_if(is.numeric,Winsorize,probs = p_w ,na.rm = TRUE)%>%
  group_by(bvdid)

@@

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
